Lattice model

### 2017-04-01 oopsla17/lattice-model.tex
various comments/questions in TODOs

\begin{defn}{(\emph{Subscript})}
  A set of $N$-dimensional points $S$ is called a \emph{subscript} if it
  satisfies:
%
\begin{equation*}
\forall i \in \textsf{Fin}(N) . \quad 
\pi_i (S) = \{p\} \wedge p \in \mathbb{Z} 
\;\;
\vee
\;\;
\pi_i (X) = \mathbb{Z} = \interv{-\infty}{\infty}{\mathsf{true}}
\end{equation*}
%
That is, the $i^{th}$ component of the set is either a singleton 
in $\mathbb{Z}$ or the infinite interval.

@@

\begin{prop}{}
  $(\region{N},\subseteq)$ is a distributive lattice.
\end{prop}
%
\begin{proof}
  Any sublattice of a distributive lattice is a distributive lattice. Power sets
  partially ordered with subset or equal to relation are distributive lattices.
  \region{N} is a subset of $\mathcal{P}{(\zinf{}^{\mkern-19mu{N}})}$ since all
  vector intervals are subsets of this power set and union and intersection
  cannot add an element that is not already in the powerset.  Inductive
  definition also ensures that \region{N} is closed under these operations.
  Therefore, \region{N} is a distributive sublattice of
  $(\mathcal{P}{(\zinf{}^{\mkern-19mu{N}})}, \subseteq)$.
\end{proof}

@@

\begin{defn}{(Extended origin)}
In $N$-dimensions, the \emph{extended origin} is the
interval vector $[-1, 1]^N$ which is a subspace of \region{N}. 
\end{defn}

\begin{defn}{(Extended origin distance)}
  We measure the \emph{extended origin distance} of an offset from the
  extended origin as the minimum number of translations by $\pm 1$ in one
  dimension at a time, to reach an offset in the extended
  origin.

This notion extends to Since an 
  offsets vector may represent infinite number of points, we measure the
  distance from the closest one.
\end{defn}
%
\begin{prop}{}
  The closed form of origin distance of an $N$ dimensional point offsets vector
  $p$ is the following:
%
  \begin{align*}
    \textit{dist}_i(p) & = \begin{cases}
      0 & \pi_i(p) = \interv{-\infty}{\infty}{} \\
      |\mathsf{a}| - 1 & \pi_i(p) = \{\mathsf{a}\} \\
    \end{cases} &
%
    |p| & = \sum_{i=1}^{N} dist_i(p)
  \end{align*}
\end{prop}
%
\begin{proof}
\end{proof}

\begin{defn}{(Close neighbourhood)}
  A point offsets vector $p'$ is said to be a close neighbour of point offsets
  vector $p$ if for every index $i$ except $j$, $\pi_i(p)$ agrees with
  $\pi_i(p')$ but at $j$, $\pi_j(p')$ is such that $|p'| + 1 = |p|$.

  This necessarily means point vectors within the extended origin and the
  degenerate point offsets vector with \interv{-\infty}{\infty}{} does not have
  close neighbours.
\end{defn}
%
\begin{prop}
  The unique close neighbour at index $i$ of an $N$ dimensional point offsets
  vector, if it exists, is given by the following partial function:
%
  \begin{align*}
    \mathit{close\_neighbour}(p,i) & = \prod^{N}_{j=1} \mathit{shift}(p,i,j) &
%
    \mathit{shift}(p,i,j) & =
      \begin{cases}
        \{a - 1\} & i = j \wedge \pi_i(p) = \{\mathsf{a}\} \wedge \mathsf{a} > 0\\
        \{a + 1\} & i = j \wedge \pi_i(p) = \{\mathsf{a}\} \wedge \mathsf{a} < 0\\
        \pi_j(p)  & otherwise
      \end{cases}
  \end{align*}
\end{prop}
%
\begin{proof}
\end{proof}

\begin{defn}{(Exact set)}
  The \emph{exact set} at origin distance $d$, $\mathit{ES}_{P,d}$, of a group
  of $N$ dimensional points $P$ is defined below:
%
  \begin{equation*}
    \mathit{ES}_{P,d} =
      \{ p \in P \mid \forall i.\
         p_i \notin \{-1,0,1\} \implies
         \exists p' \in \mathit{ES}_{P,d-1}.\ p' =
         \mathit{close\_neighbour}(p,i) \}
  \end{equation*}
%
  The overall \emph{exact set}, $\mathit{ES}_P$ is then
  $\bigcup_{1 \leq d \leq D} \mathit{ES}_{P,d}$, where $D$ is the maximum origin
  distance in $P$.
\end{defn}

>>>>

\begin{defn}{(\emph{Subscript})}
  A set of $N$-dimensional points $S$ is called a \emph{subscript} if it
  satisfies:
%
\begin{equation*}
\forall i \in \textsf{Fin}(N) . \quad 
\pi_i (S) = \{p\} \wedge p \in \mathbb{Z} 
\;\;
\vee
\;\;
\pi_i (S) = \interv{-\infty}{\infty}{\mathsf{true}}
\end{equation*}
%
That is, the $i^{th}$ component of the set is either a singleton 
in $\mathbb{Z}$ or the infinite interval.

@@

\begin{prop}{}
  $(\region{N},\subseteq)$ is a distributive lattice.
\end{prop}
%
\begin{proof}
  Any sublattice of a distributive lattice is a distributive lattice. Power sets
  partially ordered with subset or equal to relation are distributive lattices.
  \region{N} is a subset of $\mathcal{P}{(\zinf{}^{\mkern0mu{N}})}$ since all
  vector intervals are subsets of this power set and union and intersection
  cannot add an element that is not already in the powerset.  Inductive
  definition also ensures that \region{N} is closed under these operations.
  Therefore, \region{N} is a distributive sublattice of
  $(\mathcal{P}{(\zinf{}^{\mkern0mu{N}})}, \subseteq)$.
\end{proof}

@@

\begin{defn}{(Extended origin)}
In $N$-dimensions, the \emph{extended origin} is the
interval $[-1, 1]^N$ which is a subset of \region{N}. 
\end{defn}

\begin{defn}{(Extended origin distance)}
  We measure the \emph{extended origin distance} of a point from the
  extended origin as the minimum number of translations by $\pm 1$ in one
  dimension at a time, to reach a point in the extended
  origin.

This notion extends to sets of points. Since an 
   there may be an infinite number of points, we measure the
  distance from the closest one.
\todo{Mistral to check: I may have broken this notion}
\end{defn}
%
\begin{prop}{}
  The closed form of extend origin distance for a set of $N$-dimensional
  points $P$ is written as $|P|$ and is defined:
%
  \begin{align*}
|P| & = \sum_{i=1}^{N} dist_i(P)
 & 
    \textit{dist}_i(P) & = \begin{cases}
      0 & \pi_i(P) = \interv{-\infty}{\infty}{} \\
      \mathsf{a} - 1 & \pi_i(P) = \{\mathsf{a}\} \\
    \end{cases}
  \end{align*}
\end{prop}
%
\begin{proof}
\todo{Not sure what we are going to prove here? That it is a metric
space or something?}
\end{proof}

\todo{We used to call the below property contiguity, and I think this is a natural
notion- does ``close neighbour'' have some standard use or is
it okay to call this contiguity?}
\begin{defn}{(Close neighbour)}
 A set of points $P$ is said to be a \emph{close neighbour at index $j$} of a set
   $P'$ if for every index $i$ except $j$, $\pi_i(P) = \pi_i(P')$ 
 but at $j$ then $\pi_j(P) \neq \pi_i(P')$ and
 $\textit{dist}_j(P) = \textit{dist}_i(P') + 1$.

\todo{Not sure how to rewrite the following as I have a bit of hard
time parsing it.}
  This necessarily means point vectors within the extended origin and the
  degenerate point offsets vector with \interv{-\infty}{\infty}{} does not have
  close neighbours.
\end{defn}
%
\begin{prop}
  The unique close neighbour at index $i$ of an $N$-dimensional set of
  points, if it exists, is given by the following partial function:
%
  \begin{align*}
    \mathit{close\_neighbour}(p,i) & = \prod^{N}_{j=1} \mathit{shift}(p,i,j) &
%
    \mathit{shift}(p,i,j) & =
      \begin{cases}
        \{a - 1\} & i = j \wedge \pi_i(p) = \{\mathsf{a}\} \wedge \mathsf{a} > 0\\
        \{a + 1\} & i = j \wedge \pi_i(p) = \{\mathsf{a}\} \wedge \mathsf{a} < 0\\
        \pi_j(p)  & otherwise
      \end{cases}
  \end{align*}
\end{prop}
%
\begin{proof}
\todo{Hm- I guess uniqueness follows from this being a function rather
  than a relation? Seems fine no problem to prove- }
\end{proof}

\todo{On the following, add some intutition first- what is this and
  what is it for?}
\begin{defn}{(Exact set)}
  The \emph{exact set} at origin distance $d$, $\mathit{ES}_{P,d}$, of a group
  of $N$ dimensional points $P$ is defined below:
%
  \begin{equation*}
    \mathit{ES}_{P,d} =
      \{ p \in P \mid \forall i.\
         p_i \notin \{-1,0,1\} \implies
         \exists p' \in \mathit{ES}_{P,d-1}.\ p' =
         \mathit{close\_neighbour}(p,i) \}
  \end{equation*}
%
  The overall \emph{exact set}, $\mathit{ES}_P$ is then
  $\bigcup_{1 \leq d \leq D} \mathit{ES}_{P,d}$, where $D$ is the maximum origin
  distance in $P$.
\end{defn}
\todo{Ah, I think I am starting to understand, but at 
$\mathit{ES}_{P,1}$ then we end up saying there exists a 
$p'$ in $\textit{ES}_{P,0}$, but we don't calculate that set...
so how does this end?}
